---
title: "`r paste0(params$inputs$unitid, ' Sample Report')`"
format: 
  typst:
    pdf-standard: ua-1
    template: typst/template.typ
params:
  summarized_data: NULL
  inputs: NULL
---

```{r}
#| echo: FALSE
library(knitr) 
library(kableExtra) # for LaTex, and footer
library(typstable)
library(dplyr, warn.conflicts = FALSE)

table_caption <- paste0(params$inputs$kpi_name, " - ", 
                       params$inputs$irclass, 
                       if (params$inputs$irclass == "First-year") " students" else "s"
                       )
```

## About this report
This report is generated from a Quarto Markdown template as a PDF using LaTex or *Typst*. The former is well-established and supports lots of formatting but can be difficult to learn and work with, where the latter is pretty new, simpler, and suposed to be faster.

[Accessibility](https://quarto.org/docs/blog/posts/2026-03-05-pdf-accessibility-and-standards/) is ensured via [veraPDF](https://docs.verapdf.org/install/) and can support UA-2 (LaTex) or UA-1 (typst; likely later 2026 for UA-2). **If veraPDF is not installed (requires java) it still returns PDF just doesn't check it - should be pretty accessible anyway.**. The only other features that must be present are YAML title and plot or image alt text

This report is fed with data by `params`, which are populated via a module, which e.g. passes the reactively filtered data from the server to the qmd template file.

Example parameters and YAML, from the SCG:
```{r, eval=FALSE}
pagetitle: "`r paste0('NSSE', params$yr, ' Selected Comparison Groups (', params$name_nick, ')')`"
author: NSSE
output:
  html_document:
    css: styles.css
params: 
  unitid: 236939
  name_report: "Washington State University Pullman"
  name_nick: "WSU Pullman"
  yr: 25
  custom: TRUE
  suffix: "p"
```

## Content

### A table
The following is more more less what's shown in the DT::datatable call, but not interactive. If PDFs are generated with LaTex, knitr::kable and kableExtra package can be used for [table formatting](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf); for typst, use [typstable](https://cran.r-project.org/web/packages/typstable/vignettes/typstable.html). Both support spanning headers and row grouping, which should be useful.

```{r}
#| echo: FALSE
#| label: tbl-one
#| tbl-cap: !expr table_caption

x <- data.frame(params$summarized_data) |>
  rename(`Institution (n)` = 5,
         `Institution (p)` = 6,
         `Comparison (n)` = 7,
         `Comparison (p)` = 8) |>
# local testing
# x <- read.csv("C:/users/bjdugan/downloads/NSSE_data_2026-04-15.csv") |>
#   rename(`Institution (n)` = 5,
#          `Institution (p)` = 6,
#          `Comparison (n)` = 7,
#          `Comparison (p)` = 8) |>
  mutate(across(c(6, 8), \(x) as.numeric(gsub("%", "", x)) / 100 )) |>
  # table formatting (non-test)
  mutate(
    across(c(6, 8), \(x) x * 100),
    across(where(is.numeric), \(x) round(x, 1)),
         Label = paste0(Label, " [", Item, "]"), 
         Item = NULL)  
  
# add row grouping
groups <- table(x$Label)
groups <- setNames(as.integer(groups), names(groups))

# display table w/o now duplicate grouping feature
tt(x, cols = -1, rownames = FALSE) |> 
  tt_pack_rows(index = groups) |> 
  # can be named or simply listed; proportional.
  tt_widths(3, 1, 2, 2, 2, 2)
```


:::{.typst-callout kind="note"}
This text is formatted by typst into a "note" reusable component.
:::

\newpage
### A plot
Will be here.

### Headers and footers
Are defined by typst, not as Quarto chunks or elements. 
See e.g.
```{r}
readLines("inst/md/typst/header-footer.typ")
```

