---
title: "Sample Report"
format: 
  pdf:
    pdf-standard: ua-2
params:
  summarized_data: NULL
---

```{r}
#| echo: FALSE
library(knitr)
library(kableExtra)
```

## About this report
This report is generated from a Quarto Markdown template as a PDF using LaTex. [Accessibility](https://quarto.org/docs/blog/posts/2026-03-05-pdf-accessibility-and-standards/) is ensured via [veraPDF](https://docs.verapdf.org/install/) and can support UA-2 (LaTex) or UA-1 (typst; likely later 2026 for UA-2). **If veraPDF is not installed (requires java) it still returns PDF just doesn't check it - should be pretty accessible anyway.**

This report is fed with data by `params`, which are populated via a module, which e.g. passes the reactive `filtered_data()` from the server to the qmd template file.


Example parameters and YAML, from the SCG:
```{r, eval=FALSE}
pagetitle: "`r paste0('NSSE', params$yr, ' Selected Comparison Groups (', params$name_nick, ')')`"
author: NSSE
output:
  html_document:
    css: styles.css
params: 
  unitid: 236939
  name_report: "Washington State University Pullman"
  name_nick: "WSU Pullman"
  yr: 25
  custom: TRUE
  suffix: "p"
```

## Content

### A table
The following is more more less what's shown in the datatable call, but not interactive.
```{r, echo=FALSE}
params$summarized_data |> 
  kable() 
```

### A plot
Will be here.

### Child documents

The following footer section is produced as a ["child" document](https://yihui.org/rmarkdown-cookbook/child-document) containing common, often static content that might be reused across reports. These can also be toggled on and off, e.g. if footnotes are needed or not. This child includes HTML footer tag surrounding a simple code chunks that produces a production date and `unitid`.

The actual content of that footer.qmd. Note this was meant for RMD -> HTML -> PDF so this might need to be reconfigured a bit for latex.
```{r}
readLines("footer.qmd")
```

The output is rendered:
```{r, child=c("footer.qmd")}
```



